Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-10 paper.Rmd
add missing refs

Moreover, they misunderstand the use of ICEWS event data in current research. They claim that most applications to date have focused on the quad categories, but this ignores a wide swath of literature (@steinert-threlkeld:2017 and @metternich:etal:2013) that uses a specific action---such as protest---defined in the CAMEO ontology. In their article on conflict in Thailand, Metternich et alia hand-coded, for example, every actor in Thailand and focused on an analysis of how those interact.

@@

Blair & Sambanis have focused attention on comparing forecasting models and forecasts in the civil war domain.  As social science becomes more adept at predictive analysis, this will doubtless be of increasing importance.  However, these comparisons must be made carefully to ensure those correct inferences are drawn.  We continue to think that theory is overrated (@ward:2016), and that machine learning and big data will allow us to learn new things, but it will be interesting to see how the evidence for these claims are adjudicated with additional usage and careful evaluation.

>>>>

Moreover, they misunderstand the use of ICEWS event data in current research. They claim that most applications to date have focused on the quad categories, but this ignores a wide swath of literature [@steinert-threlkeld:2017; and @metternich:etal:2013] that uses a specific action---such as protest---defined in the CAMEO ontology. In their article on conflict in Thailand, Metternich et alia hand-coded, for example, every actor in Thailand and focused on an analysis of how those interact.

@@

Blair & Sambanis have focused attention on comparing forecasting models and forecasts in the civil war domain.  As social science becomes more adept at predictive analysis, this will doubtless be of increasing importance.  However, these comparisons must be made carefully to ensure those correct inferences are drawn.  We continue to think that theory is overrated [@ward:2016], and that machine learning and big data will allow us to learn new things, but it will be interesting to see how the evidence for these claims are adjudicated with additional usage and careful evaluation.
